On the Functionality of the Multilayer Perceptron

### 2020-09-03 Thesis/Source & Citations/Citations.tex
31 August 2020
- Progress on written Thesis
- Neural Network section
2 Sept 2020
- Updates to Neural Network Section of Thesis
- Added new citations

\bibitem{Liu}
Liu, Zhu, et al. "Audio Feature Extraction and Analysis for Scene Segmentation and Classiﬁcation." Journal of VLSI Signal Processing, vol. 20, 1998, pp. 61–79.

@@

@@

>>>>

\bibitem{Liu}
Liu, Zhu, et al. "Audio Feature Extraction and Analysis for Scene Segmentation and Classification." Journal of VLSI Signal Processing, vol. 20, 1998, pp. 61–79.

@@

\bibitem{Mitchell}
Mitchell, Tom Michael. Machine Learning. 1st ed., McGraw-Hill, 1997.

\bibitem{Olsen}
Olson, Harry E. \textit{Music, Physics and Engineering}. 2nd ed., Dover Publications, 1967.

@@

\bibitem{White}
White, Harvey Elliott, and Donald H. White. \textit{Physics and Music: the Science of Musical Sound}. Dover Publications, Inc., 2019.
